A Dataset of Operator-client Dialogues Aligned with Database Queries

### 2016-06-28 paper.tex
Attempt to straighten the diffs

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}
\vspace{-0.50em}
We present a new dataset of human-human task-oriented conversations in the restaurant information domain, suitable for supervised training of autonomous systems. 
Currently, the dataset contains only \OP{62} dialogues because we are still collecting more data, but we estimate we will have more than 700 dialogues until the camera ready deadline.
\OD{We are currently collecting data for the set using crowdsourcing. We have collected 62 dialogues so far; more than 700 dialogues are planned for the final version of the dataset.\footnote{\OD{We expect to release the set before the camera-ready deadline.}}}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}
\vspace{-0.50em}
We present a new dataset of human-human task-oriented conversations in the restaurant information domain, suitable for supervised training of autonomous systems. 
Currently, the dataset contains only \OP{62} dialogues because we are still collecting more data, but we estimate we will have more than 700 dialogues until the camera ready deadline.\OD{We are currently collecting data for the set using crowdsourcing. We have collected 62 dialogues so far; more than 700 dialogues are planned for the final version of the dataset.\footnote{\OD{We expect to release the set before the camera-ready deadline.}}}
